---
title: 'Obtaining and Installing'
output:
  html_document:
    keep_md: yes
    number_sections: no
    theme: spacelab
    toc: yes
  pdf_document:
    toc: yes
---

#Obtaining and installing
## Stable Version
**geoSpectral** depends on several other R packages. These packages need to be installed on your R system before you can install it. The easiest way is to install the stable [CRAN](https://cran.r-project.org/web/packages/geoSpectral/index.html) version using :
```{r eval=FALSE}
install.packages("geoSpectral")
```

The above command will automatically download and install all dependencies as well as **geoSpectral** itself. 

## Development Version
We develop and host **geoSpectral** at [Github](https://github.com/PranaGeo/geoSpectral). The *dev* branch contains the latest changes and newest features. There are two ways of getting the source code and installing it under your R installation :

### Installing from within R
You can first install the **devtools** package using the command :
```{r eval=FALSE}
install.packages("devtools")
```

If you have unresolved dependencies to other packages, you can always try to add the parameter `dependencies=TRUE` into `install.packages()`:
```{r eval=FALSE}
install.packages("devtools",dependencies=TRUE)
```

Once **devtools** package is installed, you can clone and install the *dev* branch of  **geoSpectral** using  :
```{r eval=FALSE}
require(devtools)
install_github("PranaGeo/geoSpectral", ref="dev", dependencies=TRUE)
```

Note that we had problems on our Windows machine with *devtools::install_github()* correctly building the package dependency list. 

###Installing source package from system command line
If you have *git* installed on your system, you can obtain the source code either by cloning the *git* repository from the command line of your operating system :
```
git clone -b dev https://github.com/PranaGeo/geoSpectral.git
```
or using another (GUI-based) *git* client. This will download the latest *master* branch of theThen, in your shell command prompt, try

```
R CMD INSTALL geoSpectral
```

where *geoSpectral* is the name of the folder the package source code has been downloaded by git. The above command installs the package for the current user only. If you want to install the package globally in a multi-user OS, you have to do the installation with super-user privileges. On a debian-based Linux machine, this can be achieved by prepending the command `sudo` into the previous command. For more information on how to install R packages, consult the official [R Installation and Administration](http://cran.r-project.org/doc/manuals/r-release/R-admin.html#Installing-packages) documentation.

[Back to Index](http://pranageo.com/geospectral/geospectral-tutorial)

[Previous Page (Introduction to geoSpectral)](../Introduction_to_geoSpectral/Introduction_to_geoSpectral.html)

[Next Page (The Spectra Class)](../The_Spectra_Class/The_Spectra_Class.html)