---
title: "geoSpectRal Use Cases"
output: 
  flexdashboard::flex_dashboard:
    theme: spacelab
---

Frost Prediction {.storyboard data-icon="fa-list"}
=========================================

### The problem
- Frost is a big problem for farmers
- It easy to detect that frost is happening. But it is usually too late then.
- It is harder to predict the frost before it happens.  

### 1. Data Import
- Agrotics sensors
- Dataset / Measured parameters
- Importing
- Database

```{r}
```   
 
### 2. Visualization
- Time-series graphs
- Minutely-Hourly-Daily

```{r}
plot(1:10, 3*(1:10))
```

### 3. Pre-processing
- Conversion to regular
- Eliminating bad values

```{r}
plot(1:10, 3*(1:10))
```

### 4. Modeling
- Frost Model
- Prediction

```{r}
plot(1:10, 3*(1:10))
```

### 5. Validation
- Comparison with measurements

```{r}
```

### 5. Reporting
- PDF
- Dashboard?

```{r}
```

### 6. Validation
- Comparison with measurements

```{r}
```

### 7. Sharing the results
- Excel
- Txt
- Gis

```{r}
```

Above Water Radiometry { .storyboard data-icon="fa-hashtag"}
======================================


### The problem
- Frost is a big problem for farmers
- It easy to detect that frost is happening. But it is usually too late then.
- It is harder to predict it.

### 1. Data Import
- Agrotics sensors
- Dataset / Measured parameters
- Importing
- Database

```{r}
```   
 
### 2. Visualization
- Time-series graphs
- Minutely-Hourly-Daily

```{r}
plot(1:10, 3*(1:10))
```

### 3. Pre-processing
- Matching
- Eliminating bad values

```{r}
plot(1:10, 3*(1:10))
```

### 4. Modeling
- Frost Model
- Prediction

```{r}
plot(1:10, 3*(1:10))
```