---
title: 'Plotting'
output:
  html_document:
    keep_md: yes
    theme: spacelab
    toc: yes
  pdf_document:
    toc: yes
---

```{r echo=FALSE, message=TRUE, warning=TRUE, include=FALSE}
source('Script:Plotting.R')
```

# Graphics using the traditional R way
To plot a Spectra object using the base R graphics, use spc.plot(). This method uses the R function matplot(). If there are too many observations (rows), plotting with matplot() can be very slow and may result in a figure cluttered with too many curves. To avoid such a disturbance such a case, use the argument *maxSp*. The following command will graph four spectra only, distributed evenly between the first and the last rows :


```{r fig.width=10, fig.height=5}
par(mfrow=c(1,2))
spc.plot(myS)
spc.plot(myS,maxSp=4) 
par(mfrow=c(1,1))
```

Plotting the Spectra object with respect to depth can be achieved by spc.plot.depth() :

```{r fig.width=9, fig.height=5}
par(mfrow=c(1,3))
spc.plot.depth(myS, "anap_300") 
spc.plot.depth(myS, c("anap_300","anap_500")) 
spc.plot.depth(myS, c("anap_300", "Snap"))
par(mfrow=c(1,1))
```

Plotting a Spectra object with respect to observation number (channels with respect to row index) : 

```{r fig.width=5, fig.height=5}
spc.plot.time(myS)
```

The previous command draws a maximum number of 50 channels (default maxSp=50) among all spectral data. It is also possible to draw only 7 spectra (covering the whole spectral range).

```{r fig.width=5, fig.height=5}
spc.plot.time(myS, maxSp=7) 
```

A SpcList object containing several Spectra objects can be graphed in the same page in a grid structure. The function spc.plot.grid() calls spc.plot() for every grid element. The grid panels are named according to the Station header value.
```{r}
spc.plot.grid(BL,"spc.plot", nnrow=2, nncol=2)
```

It is also possible to draw a grid of depth profiles if the dataset contains a column called *DEPTH*. The following command will plot depth profiles of 10 columns evenly distributed between the first and last columns. If  the function matches columns that have different units, a new x-axis will be drawn at the top for the additional unit. Only two units will are supported at this moment.

```{r}
spc.plot.grid(BL,"spc.plot.depth", nnrow=2, nncol=2)
```

Additional arguments that can be used to format regular plotting functions of R can also be passed :
```
spc.plot.grid(BL,"spc.plot.depth", nnrow=2, nncol=2,ylim=c(60,0)) 
```

The function spc.plot.grid() will draw only a number of maxSp columns by default. It is possible to change this behavior by setting the input argument maxSp.

```{r}
spc.plot.grid(BL,"spc.plot.depth", nnrow=2, nncol=2, maxSp=5)
```

To plot only one column per panel, make sure the name (or the column index) of the variable is passed to spc.plot.depth() through spc.plot.grid().
```{r}
spc.plot.grid(BL,"spc.plot.depth", X="anap_300",nnrow=2, nncol=2)
```

It is also possible to draw spectra from various SpcLists objects on the same graph. Overlay of Spectra plots can be achieved using spc.plot.overlay()

```{r}
spc.plot.overlay(BL,lw=2)
```


# Interactive Graphics with Javascript libraries

To plot a **Spectra** object with **plotly**, simply pass the **Spectra** object to *spc.plot.plotly()*
```{r fig.width=5, echo=TRUE, fig.height=5}
h <- spc.plot.plotly(myS)
class(h)
h
```

The variable **myS** contains data from several casts (depth profiles). To isolate a cast, we use *spc.makeSpcList()*.
```{r}
BL <- spc.makeSpcList(myS, "CAST")
```

To plot the depth profile we pass the **SpcList** object we just created to *spc.plot.depth.plotly()*
```{r fig.width=5, echo=TRUE, figh.height=5}
spc.plot.depth.plotly(BL[[4]])
```

To make a map using **rbokeh** tools, first manually load the **maps** package providing the basemap showing the continents and pass the **Spectra** object to *spc.plot.map.rbokeh()*. The 26 observations stored in this object come from a total of 4 stations which are shown in the map below :
```{r fig.width=5, echo=TRUE, fig.height=5}
library("maps")
spc.plot.map.rbokeh(myS)
```
To plot a **Spectra** object with respect to time, simply pass the object to *spc.plot.time.plotly()*
```{r fig.width=5, echo=TRUE, fig.height=5}
spc.plot.time.plotly(myS)
```


[Back to Index](http://pranageo.com/geospectral/geospectral-tutorial)

[Previous Page (Data Conversion)](../Data_Conversion/Data_Conversion.html)