---
title: 'Importing Data'
output:
  html_document:
    keep_md: yes
    theme: spacelab
    toc: no
  pdf_document:
    toc: no
---
```{r echo=FALSE, message=TRUE, warning=TRUE, include=FALSE}
source('Script:Importing_Data.R')
```

#Importing data
This section describes stages of creation of a Spectra object from data located in a csv file. The file is distributed with **geoSpectRal** and contains spectral data, a vertical profile of the particulate absorption coefficient collected at sea at discrete depth in 4 different stations. 

The first step is to create a *data.frame* object using the R function *read.table()*. We have a comma-delimited text file with several measured parameters in columns and observations from different bottles (stations and depths). 

```{r}
fnm = file.path(base::system.file(package = "geoSpectRal"),"test_data","particulate_absorption.csv.gz")
abs = read.table(fnm,sep=",",header=T)
abs$STATION=factor(abs$STATION)
abs[1:2,1:17] #Display only the first 2 rows and first 17 columns if the data frame
```
   
Ancillary (non-spectral) and spectral data are stored in columns 1-13 and 14:514 respectively. Wavelengths are extracted from column names of spectral data. The string variable *Units* stores the units of the spectral variable. The data columns were then arranged so that ancillary data are located at the right of spectral data columns. 

```{r}
lbd = as.numeric(gsub("X","",colnames(abs)[14:514]))
Units="1/m"
colnames(abs)= gsub("X",paste("anap","_",sep=""), colnames(abs))
colnames(abs)= gsub("PRES","DEPTH", colnames(abs))
abs = abs[,c(14:514,1:13)]
```

Note that we need to rename the depth column (*PRES*) so that it is called *DEPTH*. The *TIME* column needs to be an R *POSIXct* object with the right timezone information. Type `help(POSIXct)` at the R command prompt to get more information about this class.

```{r}
tz<-strsplit(as.character(abs$TIME)," ")[[1]][[3]] #Extract the timezone
abs$TIME = as.POSIXct(as.character(abs$TIME),tz=tz)
```

The *Spectra* object is created with the constructor function *Spectra()*.
```{r}
myS<-Spectra(abs,Wavelengths=lbd,Units=Units,ShortName="a_nap")
myS
```
The function Spectra() calls `spacetime::stConstruct()` that creates a `STIDF` object from an input *data.frame* object of long-table format. Type `?spacetime::stConstruct` at the R prompt for more information long and wide tables. *geoSpectRal* accepts the following column names when searching latitude and longitude information : `"Latitude"`, `"LATITUDE"`, `"lat"`, `"LAT"`, `"Longitude",`,`"LONGITUDE"`, `"lon"`, `"LON"`,`"long"`, `"LONG"`. If no suitable column is found, *LAT* and *LONG* takes the artificial value of 1. As mentioned above, Time needs to be stored in column `"TIME"`. If no such a column is found, an artificial vector sequence was created from 1 to the number of rows.  According to the way spacetime is built,  if the measurements have been performed over a time interval (instead of instantaneous measurements), the length of intervals can be specified in the column `"ENDTIME"`. If no such column is found, the data is assumed to be acquired in a time instance (`ENDTIME=TIME`).

Ancillary data is stored in the slot **\@data** while the spectral data, in slot **\@Spectra**. A spectra object could also be created with or without ancillary data. Since we will later need Ancillary data, it is best to conserve it in the case of this example. 

It is possible to inquire about the Spectra object using utility functions `dim()`, `ncol()`, `nrow()`, `names()` and `spc.colnames()`. The latter function returns the column names of spectral data, omitting those of ancillary data.
```{r}
dim(myS) 
ncol(myS) 
nrow(myS) 
tail(names(myS))
tail(spc.colnames(myS))
```

[Back to Index](http://pranageo.com/geospectral/geospectral-tutorial)

[Previous Page (The Spectra Class)](../The_Spectra_Class/The_Spectra_Class.html)

[Next Page (Accessing Data)](../Accessing_Data/Accessing_Data.html)